Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-04-26 paper-RMDON.tex
actualizacion en entrada de bibliografia y agregando un nuevo "thanks"

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Arroyo\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica}
\thanks{\IEEEauthorrefmark{1}E-mail: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}
\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

\bibitem{luo-jha}J.~Luo and N.K.~Jha, \emph{Balance the battery life and real-time issues for portable real-time embedded system by applying DVS with battery model}, IEEE/ACM International Conference on Computer Aided Design, San Jose, CA, 2000. doi: 10.1109/ICCAD.2000.896498

>>>>

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Arroyo\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica}
\thanks{\IEEEauthorrefmark{1}E-mail: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}
\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20th, 2017.}
\thanks{First draft revised on May 8th, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

\bibitem{luo-jha}J.~Luo and N.K.~Jha, \emph{Power-conscious Joint Scheduling of Periodic Task Graphs and Aperiodic Tasks in Distributed Real-time Embedded Systems}, IEEE/ACM International Conference on Computer Aided Design, San Jose, CA, 2000. doi: 10.1109/ICCAD.2000.896498
